---
title: "Assignment1"
author: "Pooja Nagaraju"
date: "2024-02-05"
output: pdf_document
---
##The follwoing link contains the link to the Dataset source: <https://www.kaggle.com/datasets/reenapinto/electric-vehicle-population-data/data>

The following packages were installed to run the following code.
```{r setup, include=FALSE}
library('tidyverse')
library(readxl)

```

Loading the dataset : 
```{r load, include=TRUE}
#evp <- load("~/mydataset.RData")
#head(evp)
evp <- read_excel("evp.xls")
head(evp)
```


The `quantitative_var` shows the desprictive statistics for the quantitative variables "Electric Range" and "Base MSRP" which includes the summary for the same
```{r quantvar}
quantitative_var <- c("Electric Range", "Base MSRP")
summary(evp[quantitative_var])
```



{r catvar} shows the descriptive statistics for the categorial variable "Electric Vehicle Type", "State","Make","Model") which gives the summary for the same

```{r catvar}
categorical_var<- c("Electric Vehicle Type", "State","Make","Model")
for(var in categorical_var){
  cat(paste("summary for", var, ":\n"))
  print(table(evp[var]))
}
```

{r transform} depicts the transformation for the variable "Electric Range" which depicts the results after the number are squared from the original variable.

```{r transformation}
evp$transformed_var<-evp$'Electric Range'^2
head(evp)
```
 
 {r hist}
This command contains the histogram graph for Legislative District which is a quantitative variable 
```{r hist}
par(mar=c(4,4,2,2))
hist(evp$'Legislative District', main="Histogram of Legislative District",xlab="Legislative District",col="black")

```
## Including Plots
The final command shows the scatterplot which has the X axis label = "Model Year", and y axis label"Electric Range")



```{r plotscatter, echo=FALSE}
plot(evp$`Model Year`,evp$`Electric Range`, main="Scatterplot", xlab= "Model Year", ylab= "Electric Range")
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
